---
title: "Exploratory Data Analysis for AVA Dataset"
author: "Jens Laufer"
date: "9 Juli 2018"
output:
  html_document:
    df_print: paged
  pdf_document: default
---

```{r setup, include=TRUE, echo=F, message=F, warning=F}
knitr::opts_chunk$set(echo = T, warning=F, message=T, fig.width = 20, fig.height = 10)
```

```{r}
library(tidyverse)
library(imager)
library(glue)
library(ggthemes)
library(scales)
library(radiant.data)
library(corrplot)
library(gridExtra)
```

```{r}
DATASET.PATH = '../data/ava_downloader/AVA_dataset'
```

```{r}
train_df <-  read_csv(glue("{DATASET.PATH}/train.csv"))
test_df <- read_csv(glue("{DATASET.PATH}/test.csv"))
```

```{r}
anti <- train_df %>% inner_join(test_df, by='image.id')
anti
```

```{r}
intersect(train_df$image.id, test_df$image.id) 
```


```{r}
show.images <-  function(n, df){
  
  layout(matrix(1:n,ncol=4,byr=T))

   for(i in seq(1,n,1)){
    image.id <- df$image.id[i]
    plot(load.image(glue("{DATASET.PATH}/images/{image.id}.jpg")))
   }
}
```


```{r}
files <- read_csv(glue("{DATASET.PATH}/image_attributes.csv")) %>% mutate(image.id = as.integer(str_sub(filename, 0, -5)))  %>% select(-filename) %>% mutate(resolution = width*height)

ava.image.dataset <- as.tibble(read_delim(glue("{DATASET.PATH}/AVA.txt"), " ", col_names = F)) 
colnames(ava.image.dataset) <- c('index', 'image.id', '1', '2', '3', '4', '5', '6', '7', '8', '9', '10','semantic.tag.id1', 'semantic.tag.id2', 'challenge.id') 
ava.image.dataset <- ava.image.dataset %>% mutate(image.id=as.integer(image.id)) %>% select(-index)


ava.image.dataset <- ava.image.dataset %>% inner_join(ava.image.dataset %>% select(-semantic.tag.id1, -semantic.tag.id2, -challenge.id) %>% gather(-image.id, key = 'rating', value = 'number')  %>% group_by(image.id) %>% summarise(rating.mean=weighted.mean(as.numeric(rating), number), rating.sd = weighted.sd(as.numeric(rating), number)) %>%  mutate(rating.mean.bucket=cut(rating.mean, breaks=1:10, labels=1:9)), by = c("image.id"))
```




## Overview


### Check for missing files



There are `r dim(files)[1]` files, but `r dim(ava.image.dataset)[1]` images in dataset.

Date entries without image file were deleted.


### Summary 


The  dataset has `r dim(ava.image.dataset)[1]` rows and `r dim(ava.image.dataset)[2]` columns. 

Columns:  `r colnames(ava.image.dataset)`


__Sample rows__

```{r}
ava.image.dataset %>% arrange(desc(image.id)) %>% head()
```



```{r}
ava.image.dataset <- ava.image.dataset %>% inner_join(files)
rm(files)
```



## Univariate Analysis




```{r}
plot.dist.num.ratings <- ava.image.dataset %>% select(image.id, 1,2,3,4,5,6,7,8,9, 10) %>% gather(-image.id, key = 'rating', value = 'number') %>%
mutate(rating=as.integer(rating)) %>% group_by(image.id) %>% summarize(number=sum(number)) %>%
  ggplot() +
  geom_histogram(aes(number), fill='steelblue', bins=50)
```

```{r}
plot.dist.rating.mean <- ava.image.dataset %>%
  ggplot() +
  geom_histogram(aes(rating.mean), fill='steelblue', bins=70) 
```

```{r}

plot.bar.rating.mean.bucket <- ava.image.dataset %>% group_by(rating.mean.bucket) %>%
  summarise(n=n()) %>%
  ggplot() +
  geom_bar(aes(rating.mean.bucket, n), fill='steelblue', stat='identity') +
  scale_y_continuous(labels=comma) +
  geom_hline(yintercept = 1000)

```


```{r}
plot.dist.aspect.ratio <- ava.image.dataset %>%
  ggplot() +
  geom_histogram(aes(aspect_ratio), fill='steelblue', bins=30)  +
  scale_x_continuous(breaks=seq(0,5,0.25))
```




```{r}
plot.dist.resolution <- ava.image.dataset %>%
  ggplot() +
  geom_histogram(aes(resolution), fill='steelblue', bins=30)  
```

```{r}

plot.dist.file.size <- ava.image.dataset %>%
  ggplot() +
  geom_histogram(aes(file_size), fill='steelblue', bins=30)  
```

```{r}

plot.dist.img.size <- ava.image.dataset %>%
  ggplot() +
  geom_histogram(aes(img_size), fill='steelblue', bins=30)  

```


```{r}

plot.dist.width <- ava.image.dataset %>%
  ggplot() +
  geom_histogram(aes(width), fill='steelblue', bins=30)  

```


```{r}

plot.dist.height<- ava.image.dataset %>%
  ggplot() +
  geom_histogram(aes(height), fill='steelblue', bins=30)  

```


```{r}

plot.dist.depth <- ava.image.dataset %>%
  ggplot() +
  geom_histogram(aes(depth), fill='steelblue', bins=30)  

```

```{r}
plot.dist.rating.sd <- ava.image.dataset %>%
  ggplot() +
  geom_histogram(aes(rating.sd), fill='steelblue', bins=30)  
```

```{r}

grid.arrange(plot.dist.rating.mean,  plot.dist.rating.sd, plot.dist.num.ratings, plot.bar.rating.mean.bucket, ncol=2)
```


```{r}
grid.arrange(plot.dist.aspect.ratio, plot.dist.file.size, plot.dist.img.size, plot.dist.width, plot.dist.height, plot.dist.depth, plot.dist.resolution, ncol=3)
```


### Best rated Images

```{r}
show.images(8, ava.image.dataset %>% arrange(desc(rating.mean)))
```

### Worst rated Images

```{r}

show.images(8, ava.image.dataset %>% arrange(rating.mean))
```

## Bivariate Analysis

```{r}
corrplot(cor(ava.image.dataset %>% select(rating.mean, rating.sd, file_size, width, height, img_size, aspect_ratio, resolution)), method = "pie")
```



```{r}
corr.rating.mean.file.size <- ava.image.dataset %>%
  ggplot(aes(x=rating.mean, y=file_size)) +
  geom_point(color='steelblue', alpha=0.4) 
```




```{r}
corr.rating.mean.img.size <- ava.image.dataset %>%
  ggplot(aes(x=rating.mean, y=img_size)) +
  geom_point(color='steelblue', alpha=0.4) 
```




```{r}
corr.rating.mean.aspect.ratio <- ava.image.dataset %>%
  ggplot(aes(x=rating.mean, y=aspect_ratio)) +
  geom_point(color='steelblue', alpha=0.4)  
```

```{r}
corr.rating.mean.resolution <- ava.image.dataset %>%
  ggplot(aes(x=rating.mean, y=resolution)) +
  geom_point(color='steelblue', alpha=0.4)  
```

```{r}
grid.arrange(corr.rating.mean.file.size, corr.rating.mean.img.size, corr.rating.mean.aspect.ratio, corr.rating.mean.resolution, ncol=2)
```




## Extraction of data for Model Iteration 1



```{r}
table(ava.image.dataset$rating.mean.bucket)
```



```{r}
ava.image.dataset$rating.mean.bucket2 <- ava.image.dataset$rating.mean.bucket 


ava.image.dataset <- ava.image.dataset %>%  mutate(rating.mean.bucket2 = replace(rating.mean.bucket2, rating.mean.bucket2==2, 3))
ava.image.dataset <- ava.image.dataset %>%  mutate(rating.mean.bucket2 = replace(rating.mean.bucket2, rating.mean.bucket2==1, 3))
ava.image.dataset <- ava.image.dataset %>%  mutate(rating.mean.bucket2 = replace(rating.mean.bucket2, rating.mean.bucket2==8, 7))
```



```{r}

table(ava.image.dataset$rating.mean.bucket2)
```
```{r}
ava.image.dataset <- ava.image.dataset %>% arrange(rating.mean) 
```

```{r}
#write.csv(ava.image.dataset, glue("{DATASET.PATH}/images_meta.csv"))
```


